### 2018-06-03 MSc_Marko_Docevski_tekst.tex
Updates from ShareLaTeX

\cite{Cope1991} Expert system EMI - Experiments in Musical Intelligence that builds on top of the Musical Dice Games invented by Haydn and Mozart. The games are based on recombining meassures, chosen from a table of meassures, by a random dice throw (or a stochastic process). EMI analyses the measures by pitches and durations and then mixes and recombines the patterns of those pitches and durations so that it generates music similar to the source material. Recombination involves pattern matching. Pattern matching should be exact, but should match musically similar patterns. EMI does this not by note pitch values, but by pitch movement and note intervals. Problems include: - how to split the source material into recombinant units, that still make sense and keep the source author/work style and harmonic structure. - how to reorder and reasemble them so that the new composition makes musical sense. Patterns are mostly 1 to 2 beats long and patterns usually start at a measure boundry. Once it detects a pattern within a composers work / corpus of a style, it creates a signature that is protected during the recombination process, so that it doesn't lose it musical meaning. After the signatures have been extracted, EMI performs hierarchical analysis on them with handwritten rules based on musical theory. Analyzed patterns are stored in lexicons according to their function. When this is done it moves on to creating music with recombination and reorganization of the patterns, using a fixed sequence of functions with free substitutions of the actual music the patterns represent. Reasembly is enchanced by using ATN (Augmented Transition Networks), a NLP technique designed to create sentences from parts stored by sentence function.

\cite{Biles1994} They only allow for 14 pitches in the melody, but those are realite, their absolute values are chose according to a mapped chrod. A chord map is created for each half measure. Each map is an array of 14 MIDI pitches. A chord is mapped to a scale strictly vertically. After a scale is selected, it is extended to 14 tones, beginning at or above middle C. Interesting representation. Due to the way chromosomes are structured, each of them must represent a musically valid measure. So a 4/4 measure must contain 8 events corresponding to each 1/8 note durations of the measure. 3 even types: new note, rest and hold. A new-note event causes a MIDI note-off followed by a note-on. A rest causes a note-off only. A hold causes nothing to happen, which has the effect of holding a note already turned on or lenghtening a rest. A hold at the begining of a measure holds whatever ended the previous measure, so rhytmic structure can blow accross boundaries. Feedback and quality function for the GA is provided manually, which is a major pain in the a. Menthor feedback / input is provided by keyboard, g for good, b for bad, with a time delay and span to account for user lag and quality listening. The GA algorythm is modified to have 'smart' mutations, i.e. they repsect musical rules. Only 6 kinds of mutations are allow, see figure 2. -- READ MORE

\cite{Zils2001} As explained above, musaics are made up of individual segments, where each segment is a sound sample from a given database. The generation problem is seen as a constraint problem on the properties of the whole sequence, as well as the properties of each segment that constitutes it. By selecting the right samples, we assign values to the segments so that all the constraints specified by the user are optimally satisfied. In a nutshell, the generation problem is defined by a set of variables (the segments of the musaic), a set of constraints weighted along their importance, with their associated cost functions which aggregate the constraints costs on variables, and a global cost function to minimize. Any wished property of the sequence can be translated into a specific constraint. There are two types of constraints: segment constraints and sequence constraints. A sequence constraint controls a property of the global sequence. These constraints can apply any set of segments, which can be the whole sequence. Contrarily to segment constraints, which are limited by the number of descriptors of the segments, the sequence constraints can be of any type, and any user can easily build up new ones. Once all the constraints are defined, the system provides another control on the sequence by associating weights to them. These weights represents how important it is to satisfy the constraint during the sequencing. There are two ways to generate the constraints. In manual
mode, the user selects all the constraints by hand, whereas in imitation mode, the segment constraints are automatically specified from a target song the user wants to rebuild: the musaic will be made of samples with the same properties as the original title’s, i.e. the same descriptors’ values. These local segment constraints are sufficient to build a musaic, but there is no guarantee on the global structure of the sequence. Therefore, to cope with this problem, the user can specify additional sequence constraints, such as continuity or distributions, etc… The system aims at generating a musaic that satisfies all the
constraints defining the sequence properties. But most of the time, the constraints cannot all be satisfied at the same time: we need to introduce a measure of the distance between the musaic and the desired sequence. Each constraint is therefore associated to cost functions evaluating its satisfaction for each segment. Building the musaic then consists in minimizing all the constraints cost functions at the same time, to fit all of the properties simultaneously.
Segment constraint cost function
Sequence constraint cost function
From constraint costs to segment cost
From segment costs to global cost
Building the musaic consists in finding a sequence out of a database of samples that best satisfies all the sequence properties defined by the constraints. When dealing with very large databases of samples, a complete search method is absolutely prohibited in order to obtain quick results. So the constraint system is solved using a local search algorithm called “Adaptive search”
Pitch constraint
Pitch and Continuity constraints, equal weights
Pitch constraint weight < Continuity constraint weigh
Percussive tempo
Combination of segment and sequence constraints
Simultaneous Pitch and Percussive Tempo constraints Pitch and 2 Simultaneous Percussive Tempo constraints

@@

>>>>

Д. Коуп во трудот \cite{Cope1991} ја опишува првата компјутерска имплементација на музичките игри со коцки. Коцките се заменети со стохастички процес. Исечоците се претставени со шаблони, кои ги добиваат со делење на корпус од пишана музика, во должини од еден до два такта. Сите шаблони се анализираат спооред рачно пишани правила базирани на музичка теорија и содржат „потпис“ на авторот и се чуваат во лексикон. Случајниот процес бира од кандидат шаблони од лексиконот коишто се компатибилни со последниот избран шаблон. Компатибилоста ја одредуваат со анализа на тон и должина на ноти и со споредба на шаблони, којашто ја врши врз основа на релативно движење на тоновите и должините.

Импелемнтација на играта со генетски алгоритам може да се види во \cite{Biles1994}. Тука исечоците се претставени со хромозоми на алгоритмот. Музиката е во строг 4/4 ритам, секој хромозом е еден такт составен од 8 настани во должина од 1/8, при што настан може да бидат нова нота, задржување на стара нота и пауза. Квалитет на секој од хромозомите при процесот на еволуција се одредува рачно од страна на човечки ментор, кој венсува вредност со помош на тастатура. Ова е очигледна болна точка за практичноста на алгоритамот, што го прави алгоритамот крајно непрактичен, потребно е многу време за вешт ментор да ги преслушува кандидатите и да ги оценува.

Во трудот \cite{Zils2001} авторите опишуваат експертски систем за креирање на мозаик од музички сегменти (исечоци). Сегментите се опишани со многжество на дескриптори. Дефинираат два вида на правила, сегментни, т.е. правила кои што се евалуираат на ниво на сегмент, и секвенцни, т.е. глобални правила, коишто се евалуираат на целата секвенца. Дел од правилата се преддефинирани, а дел корисникот на алгоритмот ги внесува рачно. Доклку сака корисникот може и да избере готова песна врз основа на која ќе се екстрахираат правила врз основа на кои ќе биде креирана нова песна, во суштина имитирајќи ја оригиналната песна од високо ниво. Бидејќи правилата не се секогаш се во согласување, авторите имаат и дефинирано постапка за евалуација на важноста на правилата врз основа на тежини, т.е. функција на чинење која ја минимизираат при процесот на генерирање.

@@

\cite{Biles1994} They only allow for 14 pitches in the melody, but those are релатив, their absolute values are chose according to a mapped chrod. A chord map is created for each half measure. Each map is an array of 14 MIDI pitches. A chord is mapped to a scale strictly vertically. After a scale is selected, it is extended to 14 tones, beginning at or above middle C. Interesting representation.
